### 2022-04-28 conclusion/conclusion.tex
more

\ourpara{SAT-inspired eliminations for superposition} We already implemented
some of the techniques described in Chapter~\ref{ch:satfol} in E. However, this
implementation is not properly tested and optimized. We plan to put finishing
touches to this implementation and test the effects of implemented preprocessing
techniques on E's performance. There are more techniques used in SAT solving,
notably bounded variable addition \cite{mhb-12-reencoding} and blocked clause
addition \cite{ok-99-er}, that we did not port to first-order logic. We want to
investigate if these techniques can be lifted to first-order logic. Lastly, we
already started work on porting existing techniques to higher-order logic.

>>>>

\ourpara{SAT-Inspired Eliminations for Superposition} We already implemented
some of the techniques described in Chapter~\ref{ch:satfol} in E. However, this
implementation is not properly tested and optimized. We plan to put finishing
touches to this implementation and test the effects of implemented preprocessing
techniques on E's performance. There are more techniques used in SAT solving,
notably bounded variable addition \cite{mhb-12-reencoding} and blocked clause
addition \cite{ok-99-er}, that we did not port to first-order logic. We want to
investigate whether these techniques can be lifted to first-order logic. Lastly,
we already started work on porting existing techniques to higher-order logic.
